A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Added pybench table.

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}

\begin{document}
\maketitle

@@

[Python bmark Table]

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=160mm]{lr-10.png}
  \caption{}
\end{figure}

>>>>

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{setspace}
\usepackage{fullpage}

\begin{document}
\maketitle
\doublespace

@@

\begin{table}
  \caption{Performance results on selected components of the PyBench suite.  We
    have ommitted the least significant performace results in terms of percent
    change.
  }
\begin{tabular}{| l | c |}
  \hline
  \textbf{Test Name} & \textbf{Performance Difference} \\ \hline
  Test Name & Performance Difference \\ \hline
  NormalClassAttribute &  19.20\% \\ \hline
  SpecialClassAttribute &  18.88\% \\ \hline
  NormalInstanceAttribute &  17.77\% \\ \hline
  StringPredicates &  15.25\% \\ \hline
  UnicodePredicates &  13.82\% \\ \hline
  SimpleListManipulation &  13.03\% \\ \hline
  CompareUnicode &  11.27\% \\ \hline
  SimpleComplexArithmetic &  10.83\% \\ \hline
  SpecialInstanceAttribute &  10.52\% \\ \hline
  TryFinally &  10.35\% \\ \hline
  CreateUnicodeWithConcat &  8.52\% \\ \hline
  StringSlicing &  6.52\% \\ \hline
  Small Performance Changes Ommitted & ... \\ \hline
  UnicodeMappings &  -1.27\% \\ \hline
  ListSlicing &  -2.40\% \\ \hline
  ComplexPythonFunctionCalls &  -3.55\% \\ \hline
  TupleSlicing &  -3.72\% \\ \hline
  WithRaiseExcept &  -5.89\% \\ \hline
  TryRaiseExcept &  -11.99\% \\ \hline
  Totals & 4.54\% \\ \hline
\end{tabular}
\end{table}

@@

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=160mm]{lr-10.png}
%   \caption{}
% \end{figure}
